### 2013-09-19 chi2014/method.tex
Fixed reversed slash on subsection

/subsection{Recruitment and Remuneration}
To study brainstorming in a crowd environment, we published brainstorming HITs (human intelligence tasks) on Amazon's Mechanical Turk. We restricted our worker pool to residents of the United States to increase the chances of English language comprehension and a shared cultural background. No other screening was performed on workers.

>>>>

\subsection{Recruitment and Remuneration}
To study brainstorming in a crowd environment, we published brainstorming HITs (human intelligence tasks) on Amazon's Mechanical Turk. We restricted our worker pool to residents of the United States to increase the chances of English language comprehension and a shared cultural background. No other screening was performed on workers.
